A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-15 text/related-work.tex
Add high-level comments.

@@

There are many papers on dependent types and most of them are affected with the pioneering work of Per Martin-L\"{o}f.
$\lambda^\Pi$\cite{Meyer1986}, Calculus of Constructions\cite{coquand:inria-00076024}, 
and Harper, Honsell and Plotkin\cite{harper1993framework} are famous papers on dependent types.
In Advanced Topics in Types and Programming Languages\cite{attapl},
a dependent type system \LLF is designed with the basis of \cite{harper1993framework}.
We adopted \cite{attapl}-like dependent types for \LMD.

>>>>

\AI{歴史をふりかえる部分もあってもいいけど，本論文との「関連」も議論す
  る必要あり．特に Brady--Hammond との比較は必須．あと，例えば他の MSP
  体系に依存型を入れるとしたらどうなりそうかの見込みを議論するとか． }

@@

There are many papers on dependent types and most of them are affected by the pioneering work of Per Martin-L\"{o}f. \AI{citation?}
$\lambda^\Pi$\cite{Meyer1986}, Calculus of Constructions\cite{coquand:inria-00076024}, 
and Harper, Honsell and Plotkin\cite{harper1993framework} are famous papers on dependent types.
In Advanced Topics in Types and Programming Languages\cite{attapl},
a dependent type system \LLF is designed with the basis of \cite{harper1993framework}.
We adopted \cite{attapl}-like dependent types for \LMD.
